A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-06-15 bioc-workflow.Rmd
clean up rep section

On the figure below, we compare the relative intensities of channels 7
to 10 on scatter plots, highlighting different marker sets. These
differences result from different peak fractions for these niches on
the mitochondrial and chromatin occupancy profiles for the two
replicates.

```{r repl1, eval = TRUE, echo=FALSE, fig.width = 12}
sel0 <- fData(hyperLOPIT)$markers != "unknown"
cls <- paste0(getStockcol(), 80)[factor(fData(hyperLOPIT)$markers)]
cls[!sel0] <- getUnknowncol()

par(mfrow = c(2, 4))
for (i in c(7, 8, 10, 9)) {
    plot(exprs(hyperLOPIT[, c(i, i+10)]), col = cls,
         main = paste("Channel", pData(hyperLOPIT)[i, "Fraction.No"]))
    points(exprs(hyperLOPIT[sel0, c(i, i+10)]), col = cls[sel0], pch = 19)
    grid()
    abline(0, 1, col = "red")
}
plot(1:100, type = "n", xaxt = "n", yaxt = "n", xlab = "", bty = "n", ylab = "")
addLegend(hyperLOPIT, fcol = "markers", where = "center", cex = .7)

i <- fData(hyperLOPIT)$markers == "Mitochondrion"
plotDist(hyperLOPIT[i, hyperLOPIT$Replicate == 2],
         featureNames(hyperLOPIT)[i], type = "l",
         mcol = "orange")
title(main = "Mitochondrion")
## plotDist(hyperLOPIT[i, hyperLOPIT$Replicate == 2])
matlines(t(exprs(hyperLOPIT[i, hyperLOPIT$Replicate == 1])), col = "#F781BF30", lty = 1)
legend("topleft", paste("Replicate", 1:2),
       col = c("#F781BF", "orange"),
       lty = 1, bty = "n")

i <- fData(hyperLOPIT)$markers == "Nucleus - Chromatin"
plotDist(hyperLOPIT[i, hyperLOPIT$Replicate == 2],
         featureNames(hyperLOPIT)[i], type = "l")
## plotDist(hyperLOPIT[i, hyperLOPIT$Replicate == 2])
matlines(t(exprs(hyperLOPIT[i, hyperLOPIT$Replicate == 1])), col = "#984EA330", lty = 1)
title(main = "Chromatin")
legend("topleft", paste("Replicate", 1:2),
       col = c("#984EA3", "steelblue"),
       lty = 1, bty = "n")
```

@@

```{r}

data(hyperLOPIT2015ms3r1)
data(hyperLOPIT2015ms3r2)
data(hyperLOPIT2015ms3r3)

hyperLOPIT2015ms3r3 <- hyperLOPIT2015ms3r3[, -(2:4)]

hll <- MSnSetList(list(hyperLOPIT2015ms3r1,
                       hyperLOPIT2015ms3r2,
                       hyperLOPIT2015ms3r3))

ij <- combn(3, 2)
pc <- apply(ij, 2,
            function(.ij) {
                tmp <- suppressMessages(commonFeatureNames(hll[.ij]))
                i <- intersect(tmp[[1]]$Fraction.No, tmp[[2]]$Fraction.No)
                diag(cor(t(exprs(tmp[[1]][, match(i, tmp[[1]]$Fraction.No)])),
                         t(exprs(tmp[[2]][, match(i, tmp[[2]]$Fraction.No)]))))
            })
names(pc) <- apply(ij, 2, paste, collapse = ".")
sapply(pc, summary)

data(hyperLOPIT2015ms3r3)
tmp <- commonFeatureNames(hyperLOPIT2015ms3r1[, -(2:4)],
                          hyperLOPIT2015ms3r3[, -(2:4)])
summary(diag(cor(t(exprs(tmp[[1]])), t(exprs(tmp[[2]])))))

data(hyperLOPIT2015ms3r3)
tmp <- commonFeatureNames(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r3)
summary(diag(cor(t(exprs(tmp[[1]])), t(exprs(tmp[[2]])))))

The third replicate was produce over 1 year after the first two by
another operator.

>>>>

<!-- On the figure below, we compare the relative intensities of channels 7 -->
<!-- to 10 on scatter plots, highlighting different marker sets. These -->
<!-- differences result from different peak fractions for these niches on -->
<!-- the mitochondrial and chromatin occupancy profiles for the two -->
<!-- replicates. -->

<!-- ```{r repl1, eval = TRUE, echo=FALSE, fig.width = 12} -->
<!-- sel0 <- fData(hyperLOPIT)$markers != "unknown" -->
<!-- cls <- paste0(getStockcol(), 80)[factor(fData(hyperLOPIT)$markers)] -->
<!-- cls[!sel0] <- getUnknowncol() -->

<!-- par(mfrow = c(2, 4)) -->
<!-- for (i in c(7, 8, 10, 9)) { -->
<!--     plot(exprs(hyperLOPIT[, c(i, i+10)]), col = cls, -->
<!--          main = paste("Channel", pData(hyperLOPIT)[i, "Fraction.No"])) -->
<!--     points(exprs(hyperLOPIT[sel0, c(i, i+10)]), col = cls[sel0], pch = 19) -->
<!--     grid() -->
<!--     abline(0, 1, col = "red") -->
<!-- } -->
<!-- plot(1:100, type = "n", xaxt = "n", yaxt = "n", xlab = "", bty = "n", ylab = "") -->
<!-- addLegend(hyperLOPIT, fcol = "markers", where = "center", cex = .7) -->

<!-- i <- fData(hyperLOPIT)$markers == "Mitochondrion" -->
<!-- plotDist(hyperLOPIT[i, hyperLOPIT$Replicate == 2], -->
<!--          featureNames(hyperLOPIT)[i], type = "l", -->
<!--          mcol = "orange") -->
<!-- title(main = "Mitochondrion") -->
<!-- ## plotDist(hyperLOPIT[i, hyperLOPIT$Replicate == 2]) -->
<!-- matlines(t(exprs(hyperLOPIT[i, hyperLOPIT$Replicate == 1])), col = "#F781BF30", lty = 1) -->
<!-- legend("topleft", paste("Replicate", 1:2), -->
<!--        col = c("#F781BF", "orange"), -->
<!--        lty = 1, bty = "n") -->

<!-- i <- fData(hyperLOPIT)$markers == "Nucleus - Chromatin" -->
<!-- plotDist(hyperLOPIT[i, hyperLOPIT$Replicate == 2], -->
<!--          featureNames(hyperLOPIT)[i], type = "l") -->
<!-- ## plotDist(hyperLOPIT[i, hyperLOPIT$Replicate == 2]) -->
<!-- matlines(t(exprs(hyperLOPIT[i, hyperLOPIT$Replicate == 1])), col = "#984EA330", lty = 1) -->
<!-- title(main = "Chromatin") -->
<!-- legend("topleft", paste("Replicate", 1:2), -->
<!--        col = c("#984EA3", "steelblue"), -->
<!--        lty = 1, bty = "n") -->
<!-- ``` -->

@@
